Relational Presentation Using Semantic Closeness\\Spatial Narrative for Mathematical Content

### 2015-05-28 Paper.tex
fix for title
tweaks

\begin{wrapfigure}{r}{0.3\textwidth}
\vspace{-28pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.28 \textwidth]{assets/final/straightMountain}
    }
\vspace{-20pt}
  \caption{Straight Learning Path}
  \label{fig:straight}
\vspace{5pt}  
      \fbox{
    \includegraphics[width=0.28 \textwidth]{assets/final/curvyMountain}
    }

  \end{center}
\vspace{-20pt}
  \caption{Curvy Learning Path}
  \label{fig:curvy}
\vspace{-10pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.45\textwidth}
\vspace{-28pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem}
    }
  \end{center}
\vspace{-20pt}
  \caption{Theorem Slide}
  \label{fig:slideP}
\vspace{-15pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{\textwidth}
\vspace{-22pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.55\textwidth]{assets/final/Architecture}
    } 
\vspace{-6pt}
  \caption{Architecture Diagram}
  \label{fig:architecture}
\vspace{0pt}
  \end{center}
\end{wrapfigure}

\begin{wrapfigure}{l}{\textwidth}
\vspace{-50pt}
\end{wrapfigure}

@@

\sys itself operates in five main steps:
\vspace{-12pt}
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Get user input for the locations and names of folders.
\item Parse \sTeX to retrieve the order of slides.
\item Extract dependencies from relational info.
\item Extract necessary XHTML or PNG parts for slides.
\item Create presentation.
\end{enumerate}
\vspace{5pt}

@@

\begin{wrapfigure}{c}{\textwidth}
\vspace{-35pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.65\textwidth]{assets/final/inclusionGraphPythagorean}
    } 
\vspace{-0pt}
  \caption{Inclusion Graph for the Pythagorean Theorem}
  \label{fig:inclusionGraph}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

\begin{wrapfigure}{l}{\textwidth}
\vspace{-50pt}
\end{wrapfigure}

In our system, the \stex files are parsed using a Depth First Search algorithm to retrieve the narrative the writer intended to use. For the explanation of the Pythagorean theorem this can be seen in \autoref{fig:inclusionGraph}. We will refer to this intended narrative layer as the \textit{primary narrative path} which we follow from slide to slide on our path to the end of the presentation. To create this primary narrative path we need to add several slides with increasing x-coordinates as portrayed in \autoref{fig:primaryNarrativePath}.

\begin{wrapfigure}{c}{\textwidth}
\vspace{-30pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.97\textwidth]{assets/final/primaryNarrativePath2}
    }
  \end{center}
\vspace{-20pt}
  \caption{Primary Narrative Path}
  \label{fig:primaryNarrativePath}
\vspace{12pt}
\end{wrapfigure}

\begin{wrapfigure}{l}{\textwidth}
\vspace{-50pt}
\end{wrapfigure}

The primary narrative path, formed by a horizontal stream of slides, is the traditional path a presenter normally uses when preparing a PowerPoint presentation. Thus it contains also temporal information which is illustrated by the arrow in \autoref{fig:primaryNarrativePath}. This temporal information is what we extracted from the \stex files as the order in which the slides (or the information on the slides) should appear.

@@

\begin{wrapfigure}{c}{\textwidth}
\vspace{-30pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo2}
    } 
\vspace{-20pt}
  \caption{Dependency Graph}
  \label{fig:depGraphPythagoreanFull}
\vspace{0pt}
  \end{center}
\end{wrapfigure}

\begin{wrapfigure}{c}{\textwidth}
\vspace{-60pt}
\end{wrapfigure}

With the data about the order and the dependencies of information within the paper, we now have an ordered information graph out of which we can build a first presentation that Annie can interact with to learn about the Pythagorean theorem. \sys creates this presentation incrementally. As outlined in \autoref{sec:narrativePaths} and illustrated in \autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order of the slides. After adding each slide it checks whether there is \textit{course-ancient} information, i.e. whether there are dependencies, for that slide. If there are dependencies those are added below the slide itself (see \autoref{fig:visualDependency}).\footnote{library impress.js was adapted to support the choosing of different paths by pressing the right or down key \cite{npentrel:npentrel15}.}

\begin{wrapfigure}{c}{1\textwidth}
\vspace{-16pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}
    } 
\vspace{-7pt}
  \caption{Visualization of Dependencies}
  \label{fig:visualDependency}
\vspace{-15pt}
  \end{center}
\end{wrapfigure}

\begin{wrapfigure}{c}{\textwidth}
\vspace{-140pt}
\end{wrapfigure}

@@

When writing a document or course notes in \stex, the creator general writes a top-level file such as \textit{notes.tex} from where other \TeX\ files are included. These included files again include further \TeX\ files etc.. Thus we are automatically provided with levels that we can use for splicing our primary narrative path into smaller narrative paths. In essence, on any level the order of information in that topic is a narrative path itself. Expressed in mathematical notation a level within a directed graph $G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the set of directed edges, is the set $L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$. From these levels we can infer the status of the information. We already know that a dependent piece of information infers that it is \textit{course-ancient} information. Anything that is on the same level or in the sublevels thereof is considered to be \textit{course-old} information.

\begin{wrapfigure}{c}{\textwidth}
\vspace{-12pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.6\textwidth]{assets/final/levels}
    } 
\vspace{-0pt}
  \caption{Inclusion Graph with Levels}
  \label{fig:levelsGraph}
\vspace{12pt}
  \end{center}
\end{wrapfigure}

\begin{wrapfigure}{l}{0.42\textwidth}
\vspace{-20pt}
  \begin{center}
  \fbox{
      \includegraphics[width=0.4\textwidth]{assets/final/60degree}
    } 
\vspace{-15pt}
  \caption [Caption for LOF]{Visualization of Dependencies and Levels at 60\degree\ \footnotemark}
  \label{fig:visualDependencyDegree}
\vspace{-24pt}
  \end{center}
\end{wrapfigure}

If Annie, while browsing through the different dependencies, realizes that she needs to refresh her memory or learn more about any of the dependent information she can enter the respective level. The presentation will then continue on that level and show all the slides from that topic in the correct order. Once Annie has gone through this short excursion, she can return to the initial slide and resume the primary narrative path. By adding a way to explore these other levels, the presentation adds more context and allows Annie to understand the subject on a deeper level. These modular excursions are included in the presentation in 3D by making use of CSS3-transitions. Thus when the user enters an excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that story line (see \autoref{fig:visualDependencyDegree}).

@@

While focusing on closeness and movement, it creates meaningful visual relations and semantic movements. The relations between the content, such as it being the next slide in the narrative or it being a dependency are shown through the closeness and the placement of the slide as well as the movements that come with it. The following movements exist:
\vspace{-12pt}
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item movement along the x-axis,
\item movement along the y-axis, and
\item rotations.
\end{enumerate}
\vspace{5pt}

>>>>

\begin{wrapfigure}{r}{0.36\textwidth}
\vspace{-2em}\centering
  \fbox{
    \includegraphics[width=0.36 \textwidth]{assets/final/straightMountain}}    \vspace{-20pt}
    \caption{Straight Learning Path}\label{fig:straight}
    \vspace{5pt}  
      \fbox{\includegraphics[width=0.37 \textwidth]{assets/final/curvyMountain}}
      \vspace{-20pt}
      \caption{Winding Learning Path}\label{fig:curvy}
      \vspace{-10pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{0.45\textwidth}\centering\vspace{-2em}
  \fbox{\includegraphics[width=0.43 \textwidth]{assets/final/slide_theorem}}\vspace{-.5em}
  \caption{Theorem Slide}\label{fig:slideP}
  \vspace{-15pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{l}{.55\textwidth}\centering\vspace{-2em}
  \fbox{\includegraphics[width=0.55\textwidth]{assets/final/Architecture}} 
  \vspace{-1em}
  \caption{Architecture Diagram}\label{fig:architecture}\vspace{-1em}
\end{wrapfigure}

@@

\sys itself operates in five main steps:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item Get user input for the locations and names of folders.
\item Parse \sTeX to retrieve the order of slides.
\item Extract dependencies from relational info.
\item Extract necessary XHTML or PNG parts for slides.
\item Create presentation.
\end{enumerate}
\vspace{5pt}

@@

\begin{wrapfigure}l{.65\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.65\textwidth]{assets/final/inclusionGraphPythagorean}} 
  \caption{Inclusion Graph for the Pythagorean Theorem}\label{fig:inclusionGraph}
\end{wrapfigure}

In our system, the \stex files are parsed using a Depth First Search algorithm to retrieve the narrative the writer intended to use. For the explanation of the Pytha\-go\-rean theorem this can be seen in \autoref{fig:inclusionGraph}. We will refer to this intended narrative layer as the \textit{primary narrative path} which we follow from slide to slide on our path to the end of the presentation. To create this primary narrative path we need to add several slides with increasing x-coordinates as portrayed in \autoref{fig:primaryNarrativePath}.

\begin{wrapfigure}{c}{\textwidth}\centering\vspace{-2em}
  \fbox{\includegraphics[width=0.97\textwidth]{assets/final/primaryNarrativePath2}}
  \vspace{-1em}
  \caption{Primary Narrative Path}\label{fig:primaryNarrativePath}
  \vspace{-1em}
\end{wrapfigure}
The primary narrative path, formed by a horizontal stream of slides, is the traditional
path a presenter normally uses when preparing a PowerPoint presentation. Thus it contains
also temporal information which is illustrated by the arrow in
\autoref{fig:primaryNarrativePath}. This temporal information is what we extracted from
the \stex files as the order in which the slides (or the information on the slides) should
appear.

@@

\begin{figure}[ht]\vspace{-1em}
  \fbox{\includegraphics[width=0.97\textwidth]{assets/final/dependencyGraphPythTheo2}} 
  \vspace{-.5em}
  \caption{Dependency Graph}\label{fig:depGraphPythagoreanFull}
\end{figure}

\begin{wrapfigure}r{.67\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.67\textwidth]{assets/final/fullPresentation2}} 
  \vspace{-1em}
  \caption{Visualization of Dependencies}\label{fig:visualDependency}
  \vspace{-1em}
\end{wrapfigure}
With the data about the order and the dependencies of information within the paper, we now
have an ordered information graph out of which we can build a first presentation that
Annie can interact with to learn about the Pytha\-go\-rean theorem. \sys creates this
presentation incrementally. As outlined in \autoref{sec:narrativePaths} and illustrated in
\autoref{fig:primaryNarrativePath}, \sys creates the primary narrative path from the order
of the slides. After adding each slide it checks whether there is \textit{course-ancient}
information, i.e. whether there are dependencies, for that slide. If there are
dependencies those are added below the slide itself (see
\autoref{fig:visualDependency}).\footnote{library impress.js was adapted to support the
  choosing of different paths by pressing the right or down key
  \cite{npentrel:npentrel15}.}

@@

\begin{wrapfigure}r{.6\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.6\textwidth]{assets/final/levels}} 
  \vspace{-1em}
  \caption{Inclusion Graph with Levels}\label{fig:levelsGraph}
\vspace{-1em}
\end{wrapfigure}
When writing a document or course notes in \stex, the creator general writes a top-level
file such as \textit{notes.tex} from where other \TeX\ files are included. These included
files again include further \TeX\ files etc.. Thus we are automatically provided with
levels that we can use for splicing our primary narrative path into smaller narrative
paths. In essence, on any level the order of information in that topic is a narrative path
itself. Expressed in mathematical notation a level within a directed graph
$G = \langle V, E \rangle $, with $V$ being a set of nodes and $E = V \times V$ being the
set of directed edges, is the set
$L_w = \lbrace v \vert \langle w, v \rangle \in E \rbrace$. From these levels we can infer
the status of the information. We already know that a dependent piece of information
infers that it is \textit{course-ancient} information. Anything that is on the same level
or in the sublevels thereof is considered to be \textit{course-old} information.

\begin{wrapfigure}{l}{0.43\textwidth}\vspace{-2em}
  \fbox{\includegraphics[width=0.4\textwidth]{assets/final/60degree}} 
  \vspace{-.5em}
  \caption[Caption for LOF]{Visualization\footnotemark of Dependencies and Levels at
    60\degree}
  \label{fig:visualDependencyDegree}
\vspace{-1em}
\end{wrapfigure}
If Annie, while browsing through the different dependencies, realizes that she needs to
refresh her memory or learn more about any of the dependent information she can enter the
respective level. The presentation will then continue on that level and show all the
slides from that topic in the correct order. Once Annie has gone through this short
excursion, she can return to the initial slide and resume the primary narrative path. By
adding a way to explore these other levels, the presentation adds more context and allows
Annie to understand the subject on a deeper level. These modular excursions are included
in the presentation in 3D by making use of CSS3-transitions. Thus when the user enters an
excursion a 90\degree\ rotation around the y-axis occurs and the user can now follow that
story line (see \autoref{fig:visualDependencyDegree}).

@@

While focusing on closeness and movement, it creates meaningful visual relations and semantic movements. The relations between the content, such as it being the next slide in the narrative or it being a dependency are shown through the closeness and the placement of the slide as well as the movements that come with it. The following movements exist:
\begin{inparaenum}[\em a\rm)]
\item movement along the x-axis,
\item movement along the y-axis, and
\item rotations.
\end{enumerate}
